Study of Higgs plus single top production using events with a same sign dimuon at the Large Hadron Collider

### 2019-12-11 presentacion_hiram/presentacion-tesis.tex
n

\begin{multicols}{2}
	\small{
\begin{itemize}
\item $t\rightarrow W^+$$^+$b$\rightarrow$ $l^+ \nu_\mu b$
\item $H\rightarrow$ $W^+$$W^-$

\begin{list}{--}{}
\item  \small{$W\rightarrow$ $l^\pm \nu$, where $l$ can be $\mu$,$e^-$  $\tau$} 
\item   \small{$W\rightarrow$ $q\bar{q'}$}
%\item \small{$W$ bosons decay leptonically resulting in a signature of two same-sign leptons }
\end{list}
\item A light-flavor quark (Forward jet)
\item  A b-jet  
\end{itemize}
}
\columnbreak
\begin{figure}
	\centering
	\includegraphics[scale=0.5]{figures/jet.png}
\end{figure}
\end{multicols}
\end{frame}

@@

\begin{frame}
\subsection{BDT}
\frametitle{Multivariable discriminator algorithm}
\small{
	A decision tree takes a set of input features and splits input data recursively based on
	those features.
	Boosting is a method of combining many weak learners (trees) into a strong classifier. The features can be a mix of categorical and continuous data.\\
	\vspace{10px}
	BDT Variables}
\tiny{
	\begin{enumerate}
		\item	$p_t$ of the sub leading leptons
		\item 	Maximum  $|\eta|$ of any  (untagged)  jet (forward jet)
		\item 	Number of jets with high $p_t$ and |$\eta$| < 2.4
		\item	Number of untagged jets with |$\eta$| > 1.0
		\item	$|\Delta\eta|$ between a forward light jet and closest lepton
		\item	$|\Delta\eta|$ between a forward light jet and a b-tagged jet
		\item 	Minimum $\Delta$R between any two leptons
		\item 	$\Delta\phi$ of the highest $p_t$ same-sign lepton pair
	%	\item	$\Delta\eta$ (most forward light jet, 2nd hardest loosely b-tagged jet)
\end{enumerate} }
\end{frame}

{\nologo
	\begin{frame}
		\frametitle{Kinematic variables}
		\Fontvi
		\begin{center}
			\begin{tabular}{cc}
				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-pt-sub} &
				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-abs-pj-eta}\\ 
				{Distribution of events of pt of the sub leading leptons} &{Distribution of selected events as a function of the jet with largest value of $|\eta|$}\\
				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variablescompare_variables-ncj24}&
				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-nfj}\\		
				{Distribution of selected events with higher pt with a |$\eta$| < 2.4 } & {Distribution of jet events for $|\eta|$>1 } \\
			\end{tabular}
		\end{center}
	\end{frame}
}

{\nologo
	\begin{frame}
	\frametitle{Kinematic variables}
		\Fontvi
		\begin{center}
			\begin{tabular}{cc}
				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-cl} &
				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-b1}\\ 
				{Distribution of events of $|\Delta\eta|$ between a forward jet and the closest lepton} & {	Distribution of events as function of $|\Delta\eta|$ between a forward jet and a b-tagged jet } \\
				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-dr}&
				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-phi}\\
				{Distribution of events with a $\Delta R$ between the lepton pairs (highest and lowest $p_t$)} & {Distribution of events of $\Delta\phi$ between the higher $p_t$ pair of leptons } \\
			\end{tabular}
		\end{center}
	\end{frame}
}

@@

 \begin{frame}
 \frametitle{Upper limit}
 \begin{table}[ht]
 {  \tiny
 		\caption[Results of $\mu$ and upper limits for SM and $k_t$=-1]{Results of $\mu$ and upper limits for Asimov extrapolations for SM and $k_t$=-1 models at 95$\%$ confidence level.}
 		\begin{tabular}{|c|c|c|c|c|}
 			\hline
 			\multirow{2}{*}{Luminosity (fb$^{-1}$)}  &\multicolumn{2}{c|}{SM ($k_t$=1)} &\multicolumn{2}{c|}{$k_t$=-1 scenario}\\
 			\hhline{~----}                        &$\mu$  &$\mu$ upper limit & $\mu$ &$\mu$ upper limit or interval\\
 			\hline
 			35.9 & 1.0 $\pm$ 7.7 & 17 & 1.0 $\pm$ 0.5 & 2.3 \\
 			\hline
 			150& 1.0 $\pm$ 6.7& 11 & 1.0 $\pm$ 0.4 &1.8\\
 			\hline
 			300&1.0 $\pm$ 4.3 &8.7 & 1.0 $\pm$ 0.3 &1.5 \\
 			\hline
 			3000&1.0 $\pm$ 1.7 & 4.3 & 1.0 $\pm$ 0.1 & 0.9-1.1\\
 			\hline
 		\end{tabular}
 		\label{upper}
                }
 	\end{table}
 \end{frame}

@@

>>>>

\begin{multicols}{2}
	\small{
\begin{itemize}
\item $t\rightarrow W^+$b$\rightarrow$ $l^+ \nu_\mu b$
\item $H\rightarrow$ $W^+$$W^-$

\begin{list}{--}{}
\item  \small{$W\rightarrow$ $l^\pm \nu$, where $l$ can be $\mu$, $e$, $\tau$} 
\item   \small{$W\rightarrow$ $q\bar{q'}$}
%\item \small{$W$ bosons decay leptonically resulting in a signature of two same-sign leptons }
\end{list}
\item A light-flavor quark (Forward jet)
\item  A b-jet  
\end{itemize}
}
\columnbreak
\begin{figure}
	\centering
	\includegraphics[scale=0.5]{figures/jet.png}
\end{figure}
\end{multicols}
\end{frame}

@@

\begin{frame}
\subsection{BDT}
\frametitle{Multivariable discriminator algorithm}
\small{
	A decision tree takes a set of input features and splits input data recursively based on
	those features.
	Boosting is a method of combining many weak learners (trees) into a strong classifier. The features can be a mix of categorical and continuous data.\\
	\vspace{10px}
	BDT Variables}
\tiny{
	\begin{enumerate}
		\item	$p_t$ of the sub leading leptons
		\item 	Maximum  $|\eta|$ of any  (untagged)  jet (forward jet)
		\item 	Number of jets with high $p_t$ >25 GeV and |$\eta$| < 2.4
		\item	Number of untagged jets with |$\eta$| > 1.0
		\item	$|\Delta\eta|$ between a forward light jet and closest lepton
		\item	$|\Delta\eta|$ between a forward light jet and a b-tagged jet
		\item 	Minimum $\Delta$R between any two leptons
		\item 	$\Delta\phi$ of the highest $p_t$ same-sign lepton pair
	%	\item	$\Delta\eta$ (most forward light jet, 2nd hardest loosely b-tagged jet)
\end{enumerate} }
\end{frame}

{\nologo
	\begin{frame}
		\frametitle{Kinematic variables}
		\Fontvi
		\begin{table}
			\centering
			\begin{tabular}{cc}
				\includegraphics[width=5.5cm,height=3.5cm]{figures/distributions/compare_variables-pt-sub} &
				\includegraphics[width=5.5cm,height=3.5cm]{figures/distributions/compare_variables-abs-pj-eta}\\ 
				{} &{}\\
				\includegraphics[width=5.5cm,height=3.5cm]{figures/distributions/compare_variablescompare_variables-ncj24}&
				\includegraphics[width=5.5cm,height=3.5cm]{figures/distributions/compare_variables-nfj}\\		
				{} & { } \\
			\end{tabular}
		\end{table}
	\end{frame}
}

{\nologo
	\begin{frame}
	\frametitle{Kinematic variables}
		\Fontvi
		\begin{center}
			\begin{tabular}{cc}
				\includegraphics[width=5.5cm,height=3.5cm]{figures/distributions/compare_variables-eta-fj-cl} &
				\includegraphics[width=5.5cm,height=3.5cm]{figures/distributions/compare_variables-eta-fj-b1}\\ 
				{} & {	} \\
				\includegraphics[width=5.5cm,height=3.5cm]{figures/distributions/compare_variables-dr}&
				\includegraphics[width=5.5cm,height=3.5cm]{figures/distributions/compare_variables-phi}\\
				{} & {} \\
			\end{tabular}
		\end{center}
	\end{frame}
}

@@

 \begin{frame}
 \frametitle{Upper limit}
 \begin{table}[ht]
 {  \scriptsize
 		\caption*{Results of $\mu$ and upper limits for Asimov extrapolations for SM and $k_t$=-1 models at 95$\%$ confidence level.}
 		\begin{tabular}{|c|c|c|c|c|}
 			\hline
 			\multirow{2}{*}{Luminosity (fb$^{-1}$)}  &\multicolumn{2}{c|}{SM ($k_t$=1)} &\multicolumn{2}{c|}{$k_t$=-1 scenario}\\
 			\hhline{~----}                        &$\mu$  &$\mu$ upper limit & $\mu$ &$\mu$ upper limit or interval\\
 			\hline
 			35.9 & 1.0 $\pm$ 7.7 & 17 & 1.0 $\pm$ 0.5 & 2.3 \\
 			\hline
 			150& 1.0 $\pm$ 6.7& 11 & 1.0 $\pm$ 0.4 &1.8\\
 			\hline
 			300&1.0 $\pm$ 4.3 &8.7 & 1.0 $\pm$ 0.3 &1.5 \\
 			\hline
 			3000&1.0 $\pm$ 1.7 & 4.3 & 1.0 $\pm$ 0.1 & 0.9-1.1\\
 			\hline
 		\end{tabular}
 		\label{upper}
                }
 	\end{table}
 \end{frame}

@@

\begin{frame}
\Huge
	Thank You
\end{frame}
